intro

### 2021-10-08 06_Paper/ER-ED/intro.Rmd
added text

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *N*-back task. 
Participants had to decide whether repeating a higher *N*-back level for larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: we have to adapt the assumption that the easiest *N*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like the objectively easiest ER strategy.
Therefore, we have to add an additional step were the option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.

>>>>

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *N*-back task. 
Participants had to decide whether repeating a higher *N*-back level for larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: we have to adapt the assumption that the easiest *N*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like the objectively easiest ER strategy.
Therefore, we have to add an additional step were the option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 EUR) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.

## Hypotheses
